Income and Food Price Transmission

### 2016-08-11 Master.Rnw
Initial changes in connection with AE rejection
JAE sub. vers.

\title{Income and Food Price Transmission\footnote{Revised version of MS 2015310 ``Income and Price Transmission''. Submitted to \emph{Agricultural Economics} for 2. round review. I thank two anonymous reviewers for their valuable comments.}}

@@

\textbf{Keywords:} price transmission, food crisis, food inflation, determinants, regression analysis, income\newpage

@@

\bibliographystyle{chicago}
\bibliography{inc_pt}

\SweaveInput{figures1.Rnw}
\newpage
\SweaveInput{tables.Rnw}
\newpage
\appendix
\SweaveInput{appendix.Rnw}

>>>>

\title{Income and Food Price Transmission}

@@

\textbf{Keywords:} price transmission, food crisis, food inflation, regression analysis, income\newpage

@@

\bibliographystyle{chicago}
\bibliography{poverty_price_transmission}

\SweaveInput{figures.Rnw}
\newpage
\SweaveInput{tables.Rnw}
\newpage
\appendix
\SweaveInput{appendix.Rnw}
